Impact of interaction network structure on community-level plant reproduction success

### 2019-02-26 paper_round2.Rmd
Comments varios.

---
title: "Impact of interaction network structure on community-level plant reproduction success"
author: "Magrach, A, Molina, FP, Bartomeus, I"
date: "6 November 2018"
output: html_document
bibliography: library.bib
csl: ecology-letters.csl
editor options:
  chunk_output_type: console
---

@@

Title: Impact of interaction network structure on community-level plant reproduction success

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species. However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014]. Understanding how changes in pollinator diversity affect whole community assemblages is thus a major challenge that requires attention.

@@

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data. Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes of interaction networks (REF, REF, REF). Even further, we now have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures (REF) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.

@@

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?). Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX). [SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM???] Each site was surveyed 7 times during the flowering season of 2015?? (February-July???) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors (IS IT JUST BEES AND HOVERFLIES?) that legitimately visited them. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the first sampling event. For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???. Our survey included a total of 19 plant species across our 16 sites.

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) functional complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with (REF). Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF). However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.

@@

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, average fruit and seed weight). We thus, had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling. We repeated this using 25% and 75% thresholds. We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable.

@@

To test this, we ran a simple simulation in which the number of species increased randomly at each time step and calculated equity in reproductive success. Instead of drawing plants randomly for each run, we tested all possible combinations for each plant number level and network, as this number is low (n = X x X = 63 possible combiations overall for the network with the largest dataset). Increasing sampling events in our simulation would only result in repeated combinations. Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities. To this end, for each species number level, we randomly combined the generated equity values across the 16 communities as to obtain one random value per species. Finally, for each of such combinations we extracted the model estimate from a linear model relating equity in relation with functional complementarity and averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other??

@@

d<-all_interactions
f<-fruitset
s<-seedset

@@

d4 <- t(d3[,1:277])
#head(d4)
#str(d4)
d5<-as.data.frame(d4)
#str(d5)
d6<-as.list(d5)

@@

At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. This is despite the fact that model 2 has a greater number of variables and should be penalized for the added complexity it represents. We will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig. XX) as well as a positive effect of the centrality of the focal plant on its fruitset.

@@

  ni<-niche.overlap(web, method="morisita")
  df <- melt(as.matrix(ni), varnames = c("row", "col"))
  df$row<-as.character(df$row)
  df$col<-as.character(df$col)

@@

library(remef)
y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs

@@

For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species). In this case, we find that none of the variables included within our model explain the differences observed.

@@

When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different individuals within a species and site we find that both model 1 and model 2 are equally good (i.e.,$\Delta AIC<2$) and thus we cannot select one over the other. Specifically, regarding the results for model 2, we find a significant and positive effect of nestedness for equity between individuals of a species (Table X, Fig. X). This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is however not maintained when using 25 and 75% thresholds. In particular, when using a 25% threshold we find model 1 is the best model and none of the variables considered are able to explain the differences observed. Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.

@@

#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.

@@

#now 75% threshold
f5.75<-subset(f3, f3$fruit.prop>0.75)
f5.75$no_rows<-rep(1, nrow(f5.75))
head(f5.75)

#NOTE TO SELF: Here is where we want to subsample 1 to 6 species per site to test the idea of increasing plants, complementarity increase.

@@

ONE QUESTION, WHY DO WE DO THIS SIMULATION ONLY FOR EQUITY AND NOT ALSO FOR AVERAGE REP SUCCESS?

@@

plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(0, 0.1) ,
     ylab = "importance of niche partitioning", xlab = "number of plants considered")

@@

#now we subsample 16 combinations at a time 100 timeas and make the average.
estimate_i <- data.frame(level = NA, estimate = NA)
estimate_k <- data.frame(level = NA, estimate = NA)
head(combinatorials_all)
for (i in 1:length(unique(combinatorials_all$Plant_number_level))){ # over levels
  temp <- subset(combinatorials_all, Plant_number_level == unique(combinatorials_all$Plant_number_level)[i])
  for(k in 1:100){ #iterations
    value <- data.frame(site = NA, eq = NA, nich = NA)
    for(j in 1:length(unique(temp$SiteID))){ # over sites
      temp2 <- subset(temp, SiteID == unique(temp$SiteID)[j]) #why only one record at Elpinar??
      value_temp <- temp2[sample(x = 1:nrow(temp2), 1),]
      value[j,1] <- value_temp$SiteID
      value[j,2] <- value_temp$equity
      value[j,3] <- value_temp$functional.comp
    } #close sites
    m <- lm(value$eq ~ value$nich)
    #plot(value$eq ~ value$nich)
    estimate_k[k,1] <- i
    estimate_k[k,2] <- m$coefficients[2]  
  } #close iteration
  #unique(estimate_k) #only 5 unique ombinations for n = 5. All negative. highly influenced by one data point of low niche part and equ = 1. "CotitodeSantaTeresa"
  #subset(f4, Site_ID == "CotitodeSantaTeresa") #Super high values!
  estimate_mean <- aggregate(estimate ~ level, estimate_k, mean)
  estimate_i[i,1] <- estimate_mean$level
  estimate_i[i,2] <- estimate_mean$estimate
  }

@@

One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough. Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure.

@@

>>>>

---
title: "Impact of interaction network structure on community-level plant reproduction success"
author: "Magrach, A, Molina, FP, Bartomeus, I"
output: html_document
bibliography: library.bib
csl: ecology-letters.csl
editor options:
  chunk_output_type: console
---

@@

Title: Impact of interaction network structure on community-level plant reproduction success  
or "Interaction network structure maximizes community-level plant reproduction success via [niche complmentariety?]()"

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species. However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure [such as...]().

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], although see [@Herrera2018] for opposite trends[IB: I think Herrea paper is not needed here, as is quite local. My 2018 Phil Trans paper sumarizs the lack of knowledge for the world]()), have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF[I only know refs for crops, e.g. winfree. Check Morris Ecology 2010 to see if there is something tehere]()). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014, [Carvalheiro et al 2014 Ecol Lett, and Mayfield ans Stouffer 2017 Nature EcoEvo]()]. Understanding how changes in pollinator diversity [diversity or interaction structure?]() affect whole community assemblages is thus a major challenge that requires attention.

@@

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data [(but see Poisot and Gravel Ecol Let?)](). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks ([Bacompte and H¿JOrdano AREES review]() REF, REF, REF) and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures ([Bascompte et al 2013 PNAS]()) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, how the structure formed by this network of interactions afects key ecosystem functions such as plant reproduction remains untested [(Winfree BAAE opinion paper is good to cite "Global change, biodiversity, and ecosystem services: What can we learn from 6 studies of pollinators?")](). The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success [and equity acorss species.]()

@@

[IB: this intro is brilliant!]()

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1?). Here, we surveyed 16 Mediterranean woodland patches, located within a XXX m2 area and with an average distance of XX km between them (min= XX, max= XX). [SHOULD WE SAY SOMETHING ABOUT THE MATRIX SURROUNDING THESE SITES OR THE TYPE OF VEGETATION PRESENT IN THEM??? IB: I don't think is relevant. ASK CURRO ABOUT THE NUMBERS ABOVE.]() Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors [IS IT JUST BEES AND HOVERFLIES? IB: NO, ALL VISITORS!]() that legitimately visited them. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 [NB: Which site has only one species!]() to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight per fruit at the end of the season. Our survey included a total of 19 different plant species across our 16 sites.

@@

At the community level, we followed the same logic as the one presented at the species level. Thus, we also calculated two network metrics providing complementary non-redundant information. In this case we focused on (i) nestedness and (ii) functional complementarity. Nestedness is the property by which specialists interact with a subset of the species that generalists interact with ([Bascompte et al 2003 PNAS]). Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness implies a certain level of redundancy and thus the possibility for functional replacement in the case of species loss (REF). [We used the widely accepted NODF metric to calculate Nestedness]() However, plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success. [To calculate functional complmentariey we used ...](). All network analysis were perfeormed using bipartite package.

@@

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, and average fruit and seed weight [IB: also scaled?]()). We thus, had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling. We repeated this using 25% and 75% thresholds. We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable. [Here is unclear how the proportion is calculated. This is: average fruit set per species is > 50%? Or as we discussed a more coplex option can be: % of species which > 50 % of individuals had seed set > 50%. Now that I see this I would only used if we gain a lot, otherwise is too complicated. Also, I removed species present is only one (or two) sites for this analysis, because the % was forces to be 1. If you kept this in your analysis, should be explained]().

@@

To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g. for n = 3 plant selected out of 6 there is only 20 possible combiations). Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities. To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrok level predictors and extracted the model estimates. We averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other?? [Curro can calculate this if needed]()

@@

d<-all_interactions
#head(d)
#I just realized here we are using all data available. 
#This is ok, but a few rare interactions are taken outside the transect (which can be removed?), and we are including focal 3' observations, which can be explained in methods.
#d <- subset(d, subset = Out != "out") #SHould we do that?
f<-fruitset
s<-seedset

@@

d4 <- t(d3[,1:ncol(d3)]) #I updated this to use defensive programming.
#head(d4)
#str(d4)
d5<-as.data.frame(d4)
#str(d5)
d6<-as.list(d5)

@@

At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed when accounting for model complexity (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which penalize for the added complexity, we will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig. XX) as well as a positive effect of the centrality of the focal plant on its fruitset.

@@

  ni<-niche.overlap(web, method="morisita") #THIS SHOULD BE EXPLAINED IN METHODS
  df <- melt(as.matrix(ni), varnames = c("row", "col"))
  df$row<-as.character(df$row)
  df$col<-as.character(df$col)

@@

#devtools::install_github("hohenstein/remef")
library(remef)
y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs

@@

For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species). However, none of the variables included within our model explain the differences observed. [show in sup mat?]()

@@

When evaluating the effect of differences in community composition and structure for equity in reproductive success across the different individuals within a species and site we find that both model 1 and model 2 are equally good (i.e.,$\Delta AIC<2$) and thus we cannot select one over the other. Specifically, regarding the results for model 2, we find a significant and positive effect of nestedness for equity between individuals of a species (Table X, Fig. X). This effect that we find when using a 50% threshold of productivity (i.e., when looking at plant species that are producing 50% of the maximum fruitset observed for the area), is however not maintained when using 25 and 75% thresholds. In particular, when using a 25% threshold we find model 1 is the best model and none of the variables considered are able to explain the differences observed. Contrastingly in the case of the 75% threshold, we find again that both model 1 and 2 are equally plausible but in this case we find a positive effect of functional complementarity between pollinators for equity in fruitset across individuals within a species.
[this is interesting, as selfing rates I expect to be ~ 40%... In any case I am confused now on this calculation]()

@@

@@

#now 75% threshold
#head(f3)
f5.75<-subset(f3, f3$fruit.prop>0.75)
f5.75$no_rows<-rep(1, nrow(f5.75))
head(f5.75)

@@

ONE QUESTION, WHY DO WE DO THIS SIMULATION ONLY FOR EQUITY AND NOT ALSO FOR AVERAGE REP SUCCESS?
Because i do not expect the average to change as dramatically when considering more species.

@@

plot(unique(combinatorials_all$Plant_number_level) , estimate, las = 1, ylim = c(-0.01, 0.1) ,
     ylab = "importance of niche partitioning", xlab = "number of plants considered")

@@

#now we subsample 16 combinations at a time 100 timeas and make the average.
estimate_i <- data.frame(level = NA, estimate = NA)
estimate_k <- data.frame(level = NA, estimate = NA)
head(combinatorials_all)
for (i in 1:length(unique(combinatorials_all$Plant_number_level))){ # over levels
  temp <- subset(combinatorials_all, Plant_number_level == unique(combinatorials_all$Plant_number_level)[i])
  for(k in 1:100){ #iterations
    value <- data.frame(site = NA, eq = NA, nich = NA)
    for(j in 1:length(unique(temp$SiteID))){ # over sites
      temp2 <- subset(temp, SiteID == unique(temp$SiteID)[j]) #why only one record at Elpinar??
      value_temp <- temp2[sample(x = 1:nrow(temp2), 1),]
      value[j,1] <- value_temp$SiteID
      value[j,2] <- value_temp$equity
      value[j,3] <- value_temp$functional.comp
    } #close sites
    m <- lm(value$eq ~ value$nich)
    #plot(value$eq ~ value$nich)
    estimate_k[k,1] <- i
    estimate_k[k,2] <- m$coefficients[2]  
  } #close iteration
  #unique(estimate_k) #only 5 unique ombinations for n = 5. All negative. highly influenced by one data point of low niche part and equ = 1. "CotitodeSantaTeresa"
  #subset(f4, Site_ID == "CotitodeSantaTeresa") #Super high values!
  estimate_mean <- aggregate(estimate ~ level, data = estimate_k, FUN = "mean")
  estimate_i[i,1] <- estimate_mean$level
  estimate_i[i,2] <- estimate_mean$estimate
  }

@@

One of the first conclusions we can extract from the fact that in most cases both of the models we considered (i.e., the simple model based on visitation metrics and the more complex one including community structure metrics) were equally good, is that for simple predictive purposes, simple visitation metrics, such as the diversity of pollinators visiting a plant, might be enough [cite Garibaldi papers using them](). Yet, a mechanistic understanding of the underlying processes requires that we take into account measures of community structure.

@@

Paragraph somewhere about the importance of how you measure functioning (average vs equity).
